### 2007-01-22 Documentation/Paper2/paper2.tex
*** empty log message ***

\begin{abstract}
We present Version 3.0 of the GLoBES (``General Long Baseline Experiment Simulator'') software, which is
a simulation tool for short- and long-baseline neutrino oscillation experiments. As new features, \GLOBESN\ allows for user-defined systematical errors, which can also be used to simulate experiments with
multiple discrete sources and detectors.
In addition, the combination with external information, such as from different experiment classes, is 
simplified. As far as the probability calculation is concerned, \GLOBES\ 
now provides an interface for the inclusion of non-standard physics without re-compilation of the software. 
The set of experiment prototypes coming with \GLOBES\ has been updated. For example, built-in fluxes are now
provided for the simulation of beta beams.
\end{abstract}

>>>>

\begin{abstract}
We present Version 3.0 of the GLoBES (``General Long Baseline Experiment Simulator'') software, which is
a simulation tool for short- and long-baseline neutrino oscillation experiments. As a new feature, \GLOBESN\ allows for user-defined systematical errors, which can also be used to simulate experiments with
multiple discrete sources and detectors.
In addition, the combination with external information, such as from different experiment classes, is 
simplified. As far as the probability calculation is concerned, \GLOBES\ 
now provides an interface for the inclusion of non-standard physics without re-compilation of the software. 
The set of experiment prototypes coming with \GLOBES\ has been updated. For example, built-in fluxes are now
provided for the simulation of beta beams.
\end{abstract}
